### 2022-02-22 documentos/math.tex
Now it's all microservices, I hope the fad persists.

\janote{Finally, we restrict Pauli diagonal maps to PCE maps, and provide a connection
between a vector subspace to the set of coefficients $\{\tau_\valpha\}$ 
in \eref{eq:PCE_definition} of a PCE quantum channel.}
{\red [anterior]
We then restrict to PCEs and, for quantum
channels, associate a vector subspace to the set of coefficients
$\{\tau_\valpha\}$ in \eref{eq:PCE_definition}.} 

@@

\janote{Cambié la eq. \eqref{eq:vectorized_pauli_strings}. Eso también
modificó la frase que le sigue a este comentario.}

>>>>

Finally, we restrict from Pauli diagonal maps to PCE maps, and provide a connection
between a vector subspace and the set of coefficients $\{\tau_\valpha\}$ 
in \eref{eq:PCE_definition} of a PCE quantum channel.
% {\red [anterior]
% We then restrict to PCEs and, for quantum
% channels, associate a vector subspace to the set of coefficients
% $\{\tau_\valpha\}$ in \eref{eq:PCE_definition}.} 

@@

% \janote{Cambié la eq. \eqref{eq:vectorized_pauli_strings}. Eso también
% modificó la frase que le sigue a este comentario.}

### 2022-02-22 documentos/pce.tex
intro
Now it's all microservices, I hope the fad persists.

\section{PCE Maps}
\janote{Propuesta: hacer un switch de títulos entre el título de II y de II.B}
\janote{En este primer agregué las referencias a en cuáles secciones hablamos de qué}
To introduce in \ref{sec:single:qubit} the family of Pauli component erasing 
maps we start in \ref{subsec:qtm_ch} reviewing basic concepts of quantum 
channels that will allow us to introduce some notation. 
% In this section we introduce the definition of Pauli component erasing maps,
% but first we go through several standard definitions needed to discuss them.
\subsection{Quantum channels} \label{subsec:qtm_ch}% {{{
Quantum channels are the most general linear operations that a quantum
system undergo independently of its past~\cite{zimansbook,cirac}.
The physical system under study will be associated with a Hilbert space
denoted by \hilbert{}, and the set of linear operators over such space will 
be denoted by $\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system
 is an element of $\mcB(\hilbert)$.

% Quantum channels comprehend the most general linear operations that a quantum
% system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
% their construction and properties, first let us define several objects. We will
% denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
% $\hilbert_d$. The set of linear operators over a Hilbert space \hilbert will
% be written as $\mcB(\hilbert)$, and the set of density operators as $\mcS(\hilbert)$.
%, the subset of density matrices as
%$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
%operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
%here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.

The construction of quantum channels includes basically three ingredients:
linearity, trace preservation and complete positivity. Linearity is needed to
map every convex combination of density matrices into a convex combination of the
evolution of such density matrices. The
trace preserving property is required for the process $\mcE$ to be
deterministic, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
Often, this condition is easy to test.
The
complete
positivity condition is needed to preserve positive semidefiniteness and handle
the non-local feature of quantum theory. 
A linear map $\mcE$ is positive if it maps density operators to density operators, \ie{}
if $\mcE[\rho]\geq 0$ for all density matrices $\rho$. 
% 
% $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ hermitian with $\Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues 
% decimos que es una matriz de densidad} \ddnote{Aqui hablamos de matrices
% positivas definidas en general, estuve revisando en varios libros, y parece que
% lo mas estandar es suponer que si se dice que es positiva (o negativa) definida
% o semi-definida, automaticamente se dice que es hermítica. Sin embargo hay
% definiciones mas generales que involucran matrices no hermiticas, esas eran las
% que yo tenía en mente (pero parece que no son tan conocidas). Opto por
% mencionar que $\Delta$ es hermítico.}. 
%
On the other hand, if one extends a positive map to include an ancilla, the resulting
map is not always positive. If, for all dimensions of the ancilla, such extension
results in a positive map, we say that the original map is completely
positive~\cite{bengtsson_zyczkowski_2017}.
Quantum channels are required to be completely positive
so as to allow the proper evolution of potentially entangled states with an 
ancilla. 
% In the other hand, a map is completely positive if extending the 
%  $\id_k \otimes \mcE$ is a positive map for $k=1,2,\dots$, where $\id_k$ is the identity channel over $\mcB(\hilbert_k)$. This ensures that every positive semidefinite operator of any
% extension of the system (where the quantum channel is now a local operation) is
% mapped to a positive semidefinite operator. The trace preserving is automatically
% fulfilled for all extensions if $\mcE$ fulfills it. Therefore, any density matrix of a system
% where $\mcE$ acts locally, is sent to a valid density matrix, this is the
% substance of complete positivity.
% \flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: E
% is totally positive if trivially extending E to the tensor product of H with an
% arbitrary dimensional ancilla space yields a positive operation.
% }\ddnote{ejecutado} 
% Concluding, quantum channels are linear completely positive trace preserving
% maps.

A simple algorithm to test the complete positivity of a quantum channel 
was developed by 
\jami{}~\cite{jamil} and Choi~\cite{choi}.
One first exploits an isomorphism that maps a channel $\mcE$ to the state
$\choi=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where
$\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is a 
maximally entangled state between the original system and an ancilla.
Remarkably, the map \mcE{} is completely positive
if and only \choi{} (also called Choi or dynamical matrix of $\mcE$) 
is positive-semidefinite~\cite{jamil,choi}.

%  the
% Bell state between two copies of \hilbert.

% Quantum channels can be characterized by means of the Choi-\jami{}
% isomorphism~\cite{choi,jamil}. This is, given a linear operation
% $\mcE:\mcB(\hilbert)\to \mcB(\hilbert)$, the so-called Choi matrix of it is
% $\choi=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$ (also called
% dynamical matrix), where
% $\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is the
% Bell state between two copies of \hilbert. The map \mcE is completely positive
% if and only \choi is positive-semidefinite.
%
%

% In fact,
% a linear operation is completely positive if and only if it has a Kraus
% representation~\cite{Kraus1983}.
% The minimum number of Kraus operators $K_i$
% needed to represent the channel is called \textit{Kraus rank}. 
%

% It can be seen from Kraus decomposition that quantum channels preserve
% hermiticity, this has a practical consequence when using hermitian bases, \ie{}
% let $\left\{ \Delta_i \right\}$ be a hermitian basis in $\mcB(\hilbert)$, then
% the entries of the matrix representation of the quantum channel $\mcE$, $\hat
% \mcE_{ij}=\tr\left( \Delta_i \mcE[\Delta_j] \right)$, are real. In particular,
% in this work we are interested in systems of $N$ qubits, and we use hermitian
% bases consisting of the so-called \textit{Pauli strings} \ddnote{aqui
% introduzco el nombre estandar}, defined as 
% \begin{equation}
% \sigma_{\vec \alpha}:=\sigma_{\alpha_1}\otimes \sigma_{\alpha_2} \otimes \dots \otimes \sigma_{\alpha_N},
% \label{eq:pauli_strings}
% \end{equation}
% where $N$ is the number qubits, $\alpha_i=0,1,2,3$ with $\sigma_0:=\one$ and
% $\sigma_{1,2,3}:=\sigma_{x,y,z}$. Thus, given $N$ and the fact that $\tr
% \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$, it is clear that the
% basis $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ is orthonormal in
% $\mcB(\hilbert_{2^N})$. The case with $N=1$ corresponds to the well-known
% \textit{Pauli basis},
% $1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$.

%

% \flnote{
% probablemente convenga mostrar la ecuaci'on desplegada. Asimismo se debe decir que 
% $\sum_i K_i^\dagger K_i = 1$ para la trace-preserving property. 
% Creo qie ``hermiticity preserving'' es en parte consecuencia de la definición, pero esto no es muy importante
% }\ddnote{ejecutado, hacia falta edicion, sin embargo lo de hermiticity preserving es para hacer incapie en por que podemos trabajar en una representacion totalmente real de los canales.}
% 
%   \ddnote{[Choi representation, Kraus operators and Stinespring dilation]}

% }}}
\subsection{Pauli component erasing maps} % {{{
\label{sec:single:qubit}
% \todo{David escribe una primera version y luego Carlos itera}
\janote{Se añadió un primer párrafo para hacer una transición suave del A
al B y decir qué discutimos aquí.}
Now that we have discussed the main features of quantum channels
we are going to introduce the Pauli component erasing maps.
We shall start exploring the single qubit scenario 
and continue with the $N$-qubit case.

The most general single qubit density matrix can be written as
\begin{equation}
% \rho=\frac{\one +\vec r \cdot \vec \sigma}{2}.
\rho=\frac12 {\sum_{\alpha=0}^3 r_\alpha \sigma_\alpha},
\end{equation}
with $\sigma_0= \one$, and $\sigma_{1,2,3}$ the usual Pauli matrices. 
Normalization requires that $r_0=1$ and the remaining $r_{1,2,3}$ 
form the Bloch vector. Consider the map that projects
each component 
in the following way,
\begin{equation}
r_\alpha \mapsto \tau_\alpha r_\alpha
\end{equation}
where $\tau_\alpha$ is either $1$ or $0$ (trace preserving requires
that $\tau_0=1$). Not every
such operation  is a quantum map; for example, collapsing the entire Bloch
ball to the $xy$ plane (setting $\tau_{1,2}=1$ and  $\tau_3=0$) is not a quantum
channel. A direct evaluation of the complete positivity
conditions~\cite{zimansbook,davalosdivisibility}, 
\begin{align}
1+\tau_1+\tau_2+\tau_3 &\geq 0, \nonumber \\
1+\tau_\alpha-\tau_\beta-\tau_\gamma &\geq 0 \ \ \forall \alpha\neq \beta \neq \gamma,
\end{align}
where trace-preserving is already imposed, show that five out of
the eight 1-qubit PCE maps are quantum channels.
% 
% show that only five
% operations are \pce:
% \janote{Derivado de mi comentario sobre el uso de ``PCE maps''
% también propongo que en vez de ``show that only five operations are \pce{}''
% se cambie por ``show that five out of the eight 1-qubit PCE maps are quantum
% channels''} 
These operations are the identity map, the completely depolarizing channel
($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip
channels~\cite{chuangbook}, 
% These operations are by definition diagonal in the
% Pauli basis~\cite{Ziman2005,davalosdivisibility}, \ie{} $\hat
% \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$
and can be pictured using one column tables showing the positions of $0$s and
$1$s, see~\fref{fig:one:qubit:examples}.

@@

	\caption{\janote{Le modificamos la primera frase a esta caption para que la Fig sea
	autocontenida}

@@

total depolarization, respectively. In (e) we show a map that only erases the component
$r_1$, collapsing the Bloch sphere into a disk, and thus does not correspond to a quantum operation.}

@@

A Pauli component erasing (PCE) map is a map
%  Pauli diagonal operation
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
For the operation to be trace preserving, it is required that $\tau_{\vec
0}=1$. 
It is worth noticing that, as for the single qubit case, not all PCE maps are
quantum operations. 
On the other hand, constructing and
evaluating the conditions for complete positivity is involved and is the main
problem addressed in this paper. 
We shall refer to the map  $\paulicomponents \mapsto \taus \paulicomponents$, 
with arbitrary values of 
% but allow the 
$\taus$ (only restricted by complete positivity) as {\it Pauli diagonal operations}.

@@

A graphical representation for PCE maps may be introduced, being the
two qubits case what has proved to be the most useful. Consider a $N$ dimensional 
Cartesian grid, with $4^N$ places.  Each place has $N$ integer coordinates, ranging
from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
\eref{eq:N_qubits_rho}. For a given PCE, we shall fill 
the square if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
empty. Examples for $N=1$ are provided in \fref{fig:one:qubit:examples}, whereas
for two qubits, we exemplify them in \fref{fig:two:qubit:examples}.

It is worth noticing that the set of \pce{} maps overlaps with the set
of ``Pauli diagonal channels constant on axes'' defined in
Ref.~\cite{nathanson2007pauli}, consisting of convex combinations of
\textit{quantum-classical} channels. In particular, it can be shown that
quantum-classical channels defined with the eigenbasis of some set of $2^N-1$
commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $
2^N $ components equal to $1$s in its diagonal, see appendix~\sref{quantum_classical}.

>>>>

\section{Pauli component erasing maps}
\label{sec:pce_maps}
% \janote{Propuesta: hacer un switch de títulos entre el título de II y de II.B}
% \janote{En este primer agregué las referencias a en cuáles secciones hablamos de qué}
% To introduce in \ref{sec:single:qubit} the family of Pauli component erasing 
% maps we start in \ref{subsec:qtm_ch} reviewing basic concepts of quantum 
% channels that will allow us to introduce some notation.

% \afnote{Propongo que cambiemos el inicio de esta sección por: 
In this section we introduce the family of Pauli component erasing (PCE)
\cpnote{Revisar despues de escribir la intro que no se ha introducido la sigla}
maps. Let us start our discussion with a brief review of several basic concepts
of quantum channels that will allow us to introduce some notation, 
and finish with the definition of PCE maps, some generalities. We further 
introduce a useful graphical representation  for them.
% of the aforementioned maps. 
% and finish with the definition of PCE maps, some generalities and a graphical representation. 
% }
% In this section we introduce the definition of Pauli component erasing maps,
% but first we go through several standard definitions needed to discuss them.
\subsection{Quantum channels} \label{subsec:qtm_ch}% {{{
% \afnote{Creo que podríamos empezar la sección introduciendo el espacio de
% Hilbert y esas cosas y después si dedicarse solamente a Quantum channels. Si
% están de acuerdo, entonces sólo tendriamos que cambiar el orden de las dos
% primeras frases en el primer párrafo.}
Quantum channels are the most general linear operations that a quantum system
undergo independently of its past~\cite{zimansbook,cirac}.  The physical system
under study will be associated with a Hilbert space denoted by \hilbert{}, and
the set of linear operators over such space will be denoted by
$\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system is an
element of $\mcB(\hilbert)$.
% \afnote{En esta última parte podriamos cambiar asi:}
% \afnote{The state of the physical system under study is associated to a
% Hilbert space \hilbert{}, and the set of linear operators over such space is
% denoted by $\mcB(\hilbert)$. In this way, a density matrix $\rho$ of such
% system is an element of $\mcB(\hilbert)$.}
% Quantum channels comprehend the most general linear operations that a quantum
% system undergo independently of its past~\cite{zimansbook,cirac}. To introduce
% their construction and properties, first let us define several objects. We will
% denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as
% $\hilbert_d$. The set of linear operators over a Hilbert space \hilbert will
% be written as $\mcB(\hilbert)$, and the set of density operators as $\mcS(\hilbert)$.
%, the subset of density matrices as
%$\mcS(\hilbert)$, which is in turn a subset of the so called trace-class
%operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied
%here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.

The construction of quantum channels includes basically three ingredients:
linearity, trace preservation and complete positivity. Linearity is needed to
map every convex combination of density matrices into a convex combination of the
evolution of such density matrices. The
trace preserving property is required for the process $\mcE$ 
 to happen with probability $1$, and reads $\tr\mcE[\rho]=\tr \rho =1$. 
Often, this condition is easy to test.
The
complete
positivity condition is needed to preserve positive semidefiniteness and handle
the non-local nature of quantum theory.
A linear map $\mcE$ is positive if it maps density operators to density operators, \ie{}
if $\mcE[\rho]\geq 0$ for all density matrices $\rho$. 
% 
% $\mcE[\Delta]\geq 0 \ \ \forall \Delta \in \mcB(\hilbert)$ hermitian with $\Delta\geq 0$\cpnote{Francois, de tu nota, la $\Delta$ ya es hermitica, pues 
% decimos que es una matriz de densidad} \ddnote{Aqui hablamos de matrices
% positivas definidas en general, estuve revisando en varios libros, y parece que
% lo mas estandar es suponer que si se dice que es positiva (o negativa) definida
% o semi-definida, automaticamente se dice que es hermítica. Sin embargo hay
% definiciones mas generales que involucran matrices no hermiticas, esas eran las
% que yo tenía en mente (pero parece que no son tan conocidas). Opto por
% mencionar que $\Delta$ es hermítico.}. 
%
On the other hand, if one extends a positive map to include an ancilla, the resulting
map is not always positive. If, for an ancillary system of arbitrary dimension, such extension
results in a positive map, we say that the original map is completely
positive~\cite{bengtsson_zyczkowski_2017}.
Quantum channels are required to be completely positive
so as to allow the proper evolution of potentially entangled states with an
ancilla; to test this condition we require some additional steps. 
% \afnote{Sería bueno mencionar también que la tarea de determinar la CP
% de un mapa es no trivial, lo que sirviría también como conector o preambulo del
% siguiente párrafo.}
% In the other hand, a map is completely positive if extending the 
%  $\id_k \otimes \mcE$ is a positive map for $k=1,2,\dots$, where $\id_k$ is the identity channel over $\mcB(\hilbert_k)$. This ensures that every positive semidefinite operator of any
% extension of the system (where the quantum channel is now a local operation) is
% mapped to a positive semidefinite operator. The trace preserving is automatically
% fulfilled for all extensions if $\mcE$ fulfills it. Therefore, any density matrix of a system
% where $\mcE$ acts locally, is sent to a valid density matrix, this is the
% substance of complete positivity.
% \flnote{No creo que lo de Bell state sea conveniente. Mejor decir algo como: E
% is totally positive if trivially extending E to the tensor product of H with an
% arbitrary dimensional ancilla space yields a positive operation.
% }\ddnote{ejecutado} 
% Concluding, quantum channels are linear completely positive trace preserving
% maps.

A simple algorithm to test the complete positivity of a quantum channel 
was developed by 
\jami{}~\cite{jamil} and Choi~\cite{choi}.
One first exploits an isomorphism that maps a channel $\mcE$ to the state
$\choi=\left(\id \otimes \mcE\right)[\proj{\Omega}{\Omega}]$, where
$\ket{\Omega}=1/\dim(\hilbert)\sum_i^{\dim(\hilbert)}\ket{i}\ket{i}$ is a 
maximally entangled state between the original system and an ancilla and
``$\id$'' is the identity channel.
Remarkably, the map \mcE{} is completely positive
if and only \choi{} (also called Choi or dynamical matrix of $\mcE$) 
is positive-semidefinite~\cite{jamil,choi}. 
% \afnote{No sé si es algo obvio, pero creo que seria bueno comentar que es el objeto $\id$.}
%  the
% Bell state between two copies of \hilbert.

% }}}
\subsection{Structure of PCE maps} % {{{
\label{sec:single:qubit}
% \todo{David escribe una primera version y luego Carlos itera}
% Now that we have discussed the main features of quantum channels
% we are going to introduce the Pauli component erasing maps.
% We shall start exploring the single qubit scenario 
% and continue with the $N$-qubit case. 
% 
% \afnote{
We have discussed the main features of quantum channels, now
we turn our attention to introduce the Pauli component erasing maps. We start
by exploring the single qubit scenario and then we treat the $N$-qubit case.
% }

The most general single qubit density matrix can be written as
\begin{equation}
% \rho=\frac{\one +\vec r \cdot \vec \sigma}{2}.
\rho=\frac12 {\sum_{\alpha=0}^3 r_\alpha \sigma_\alpha},
\end{equation}
% \afnote{Creo que este párrafo queda mejor así: where
% $\{\sigma_{0},\sigma_{1},\sigma_{2},\sigma_{3}\}=\{\one,\sigma_{x},\sigma_{y},\sigma_{z}\}$,
% with $\one$ the $2\times 2$ identity matrix and $\sigma_{j}$ the usual Pauli
% matrices. Note that normalization requires that $r_0=1$. On the other hand, the
% remaining $r_{j}$ coefficients constitute the so called Bloch vector
% $\vec{r}=(r_{x},r_{y},r_{z})$. Consider the map that projects each component in
% the following way:}
% 
with $\sigma_0= \one$, and $\sigma_{1,2,3}$ the usual Pauli matrices.  
Normalization requires that $r_0=1$ and the remaining $r_{1,2,3}$ 
form the Bloch vector. 
Consider the map that projects
each component 
in the following way,
% 
\begin{equation}
r_\alpha \mapsto \tau_\alpha r_\alpha
\label{EqPCE}
\end{equation}
where $\tau_\alpha$ is either $0$ or $1$ (trace preserving requires
that $\tau_0=1$). 
From now on we refer to any operation like that described in
\eref{EqPCE}, as single qubit \textit{Pauli component erasing} (\pce{}) maps.
Not every such operation  is a quantum channel;
for example, collapsing the entire Bloch ball to a disk on the $xy$
plane ($\tau_{1}=\tau_{2}=1$ and  $\tau_3=0$) 
leads
to a violation of the CP conditions. Indeed a direct evaluation
of such conditions yield~\cite{zimansbook,davalosdivisibility}, 
% 
% 
% is not a quantum channel
% \afnote{(Aquí podemos colocar en vez de ``is not a quantum channel'', ``leads
% to a violation of the CP conditions, indeed a direct evaluation
% \cite{zimansbook,davalosdivisibility}'')}. A direct evaluation of the complete
% positivity conditions~\cite{zimansbook,davalosdivisibility}, 
\begin{align}
1+\tau_1+\tau_2+\tau_3 &\geq 0, \nonumber \\
1+\tau_\alpha-\tau_\beta-\tau_\gamma &\geq 0 \ \ \forall ~\alpha\neq \beta \neq \gamma,
\end{align}
where trace-preserving is already imposed, show that five out of
the eight 1-qubit PCE maps are quantum channels.
% 
% show that only five
% operations are \pce:
% \janote{Derivado de mi comentario sobre el uso de ``PCE maps''
% también propongo que en vez de ``show that only five operations are \pce{}''
% se cambie por ``show that five out of the eight 1-qubit PCE maps are quantum
% channels''} 
These operations are the identity map, the completely depolarizing channel
($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip
channels~\cite{chuangbook}, 
% These operations are by definition diagonal in the
% Pauli basis~\cite{Ziman2005,davalosdivisibility}, \ie{} $\hat
% \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$
and can be pictured using one column tables showing the positions of $0$s and
$1$s, see~\fref{fig:one:qubit:examples}.

@@

	\caption{
% \janote{Le modificamos la primera frase a esta caption para que la Fig sea
% 	autocontenida}

@@

total depolarization, respectively, 
as the color of each square indicates the value attained by the corresponding
$\tau_{\alpha}$, either 0 (white) or 1 (black). 
In (e) we show a map that only erases the component
$r_1$, collapsing the Bloch sphere into a disk, and thus does not correspond to
a quantum operation.
% \afnote{Propongo el siguiente caption: (a) Pictorial
% representation of a single qubit \pce{} map.
% The color of each square indicates the value attained by the corresponding
% $\tau_{\alpha}$, either 0 (white) or 1 (black). The diagrams in (b), (c) and
% (d) correspond to the identity map, dephasing channel, and total
% depolarization, respectively. In (e) we show a map that only erases the
% component $r_1$, collapsing the Bloch sphere into a disk, and thus does not
% correspond to a quantum operation.}
}

@@

% Thus, i
In general, a Pauli component erasing (PCE) map is a map
%  Pauli diagonal operation
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
In addition, for the operation to be trace preserving, it is required that $\tau_{\vec
0}=1$. 
It is worth noticing that, as for the single qubit case, not all PCE maps are
quantum operations. 
On the other hand, constructing and
evaluating the conditions for complete positivity is non-trivial and is the main
problem addressed in this paper.
We shall refer to the map  $\paulicomponents \mapsto \taus \paulicomponents$, 
with arbitrary values of 
% but allow the 
$\taus$ (only restricted by complete positivity) as {\it Pauli diagonal operations}.

@@

A graphical representation for PCE maps may be introduced, being the
two qubits case what has proved to be the most useful. Consider a $N$ dimensional 
Cartesian grid, with $4^N$ places.  Each place has $N$ integer coordinates, ranging
from 0 to 3, so each place corresponds to a given $\vec \alpha$ in 
\eref{eq:N_qubits_rho}. For a given PCE, we shall fill  \janote{Jose Alfredo quizá itera}
the square if the corresponding $\tau_{\vec \alpha}=1$. Otherwise, we leave it 
empty. 
Examples for $N=1$ and $N=2$ are provided in \fref{fig:one:qubit:examples} and
\fref{fig:two:qubit:examples}, respectively.

It is worth noticing that the set of \pce{} maps overlaps with the set
of ``Pauli diagonal channels constant on axes'' defined in
Ref.~\cite{nathanson2007pauli}, consisting of convex combinations of
\textit{quantum-classical} channels. In particular, it can be shown that
quantum-classical channels defined with the eigenbasis of some set of $2^N-1$
commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $
2^N $ components equal to $1$s in its diagonal.
% \afnote{Aquí me parece que falta información. Creo que hay que decir que es lo
% que es diagonal y en que base.} 
For details, we refer the reader to appendix~\ref{quantum_classical}.

### 2022-02-22 documentos/vector_space.tex
Comentarios apéndice Alejo y otra cosa chiquita
I transformed a bug into a feature. Once you learn how, you'll never forget it
Now it's all microservices, I hope the fad persists.

\subsection{PCE quantum channels as vector spaces} % {{{
\cpnote{Ojo, cambie el nombre de la seccion. Pendiente de sus comentarios}
% \ddnote{propongo channels as vector spaces como titulo de seccion, pues lo
% actual se entiende mas en el sentido estandar: canales como miembros de un
% espacio vectorial, que tambien es cierto, pero no es el punto aqui}
% \cpnote{Falta lo de las clases de equivalencias, pero aun no encuentro el
% espacio. Quizá cuando haga falta se puede poner}
% \janote{Se me hace que podemos agregar algo al final, ya que es la parte en la que
% se hablan de la regla $2^k$ y regla espejo. No tengo una idea clara, pero si te 
% parece una buena idea podría elaborar más cómo meterlo ahí}
% \par
% Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{

In this subsection we will provide a one-to-one relation between PCE quantum
channels and the subspaces of a discrete vector subspace associated with the
indices $\valpha$ labeling the components of a state; see
\eref{eq:N_qubits_rho}. \cpnote{Some established facts about vector spaces will allow
us to draw conclusions for PCE quantum channels.}
\janote{Prefiero esta frase:}
\janote{Some established facts about vector spaces will allow
us to derive the main features of PCE quantum channels.}

@@

\cpnote{Revisar, solo tiene una iteracion por parte mia}
Examples of diagrams for several PCE quantum channels. In
 (a) the totally depolarizing channel is represented whereas
in (b) a PCE channel that preserves four components.  (c), (d)
and (e) show three generators \cpnote{Quizá poner los nombres de los generadores acá}; the combination of any two of them
yields the channel in (b). (f) represents the identity map. 

@@

>>>>

\subsection{PCE quantum channels as vector spaces} % {{{
% \cpnote{Ojo, cambie el nombre de la seccion. Pendiente de sus comentarios}
% \ddnote{propongo channels as vector spaces como titulo de seccion, pues lo
% actual se entiende mas en el sentido estandar: canales como miembros de un
% espacio vectorial, que tambien es cierto, pero no es el punto aqui}
% \cpnote{Falta lo de las clases de equivalencias, pero aun no encuentro el
% espacio. Quizá cuando haga falta se puede poner}
% \janote{Se me hace que podemos agregar algo al final, ya que es la parte en la que
% se hablan de la regla $2^k$ y regla espejo. No tengo una idea clara, pero si te 
% parece una buena idea podría elaborar más cómo meterlo ahí}
% \par
% Inversion de la relacion entre tau y p, y que las probablidiades deben ser positivas {{{

In this subsection we will provide a one-to-one relation between PCE quantum
channels and the subspaces of a discrete vector subspace associated with the
indices $\valpha$ labeling the components of a state; see
\eref{eq:N_qubits_rho}. 
Some established facts about vector spaces will allow
us to derive the main features of PCE quantum channels.

@@

% \cpnote{Revisar, solo tiene una iteracion por parte mia}
% Examples of diagrams for several 2-qubit PCE quantum channels: (a) the totally
% depolarizing channel, (b) a PCE channel that preserves four components.
% (c), (d) and (e) show three generators \cpnote{Quizá poner los nombres de los
% generadores acá}; the combination of any two of them yields the channel in (b).
% (f) represents the identity map. 

@@

Examples of diagrams for several 2-qubit PCE quantum channels: (a) the totally
depolarizing channel, (b) a PCE channel that preserves four components, the
normalization component, one local component of qubit 2 and two correlations between the 
two qubits.
(c), (d) and (e) show the three generators $\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and
$\mcG_{(2,2)}$, respectively; the combination (overlap of diagrams) of any two
of them yields the channel in (b).
(f) represents the identity map. 
